\documentclass[11pt,a4paper]{moderncv}
\moderncvtheme[blue]{casual}
\usepackage[T1]{fontenc}
\usepackage[applemac]{inputenc}
\usepackage[croatian]{babel}
\usepackage[scale=0.8]{geometry}
\recomputelengths

\renewcommand*{\mobilephonesymbol}   {}

% personal data
\firstname{Alexander}
\familyname{Huras}
\mobile{415.699.8293}
\email{alex.huras@gmail.com}
\extrainfo{Github: athuras}
\extrainfo{twitter: @athuras}
%\photo[84pt]{placeholder.jpg}   % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted

\nopagenumbers{}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\renewcommand*{\emailsymbol}{}
\renewcommand*{\mobilesymbol}{}
\maketitle

%Section
\section{Hi There!}
\cvline{}{\Large I find patterns and solve problems.}
\cvline{}{
\small I'm continually seeking \textbf{interesting}, and \textbf{challenging} work, with people who share that goal.
I have a broad collection of experience that spans industries and disciplines with a recent focus on distributed systems, functional programming, and statistics.
My ideal team is one where I can learn at least as much as I can teach.
}

%Section
\section{Skills}
\cvcomputer{Languages}{Scala, Python, Erlang, Julia, Haskell}{Platforms}{Hadoop, Aurora + Mesos, Unix, AWS}
\cvcomputer{Tools}{Scalding, Finagle, Storm, NumPy, Thrift}{Interests} {Functional Programming, Idris, Applied Statistics, Linear Algebra}

%Section
\section{Experience}

\cventry{August 2014 -}{Twitter Inc.}{Software Engineer (Ads Data Infrastructure)}{San Francisco, CA}{}{
  I've worked on search engines, federated databases, and a large scale timeseries reporting system, with a primary focus on interactive ad-campaign performance forecasting.
  I've written numerous Scalding jobs, and substantially contributed to many revenue-critical production systems deployed on thousands of nodes.
  I worked primary in \textbf{Scala}, and \textbf{Python} (with some Java thrown in); and developed an addiction to functional programming along the way.
  I've guided complete system lifecycles, from deprecating and shutting down large legacy projects, to designing their newer, sexier replacements.
  I have personally deleted tens of thousands of lines of old/crufty code.
  I consistently give excellent code reviews (references available upon request).
}

\cventry{Spring 2013}{Facebook Inc.}{Product Analytics Intern}{Menlo Park, CA}{}{
	I munged data, and conducted/analysed experiments for what is now the Growth/Messages analytics team, I had ownership of the Push Notification data pipelines.
  My most significant contribution was a large refactor/redesign of a legacy reporting pipeline---the result ran an order of magnitude faster, using 20\% of the resources.
}

\cventry{Fall 2012}{Magnetic Inc.}{Data Engineer}{New York City, NY}{}{
	I built multiple analytics, and modelling pipelines with \textbf{Hadoop, Pig, AWS} and various flavors of \textbf{Python}.
	Additionally, I built some NLP tools targeted at assessing search data quality. All of which are happily operating in production.
}

\cventry{Winter 2012}{SkyGrid Inc.}{Software Engineering Intern}{Sunnyvale CA}{}{
	As part of a small team I wore many hats. I contributed to the iOS codebase for Touchtv, a social TV app for iPad wherein I was responsible for Facebook and Twitter integration.
}

\cventry{Spring 2011, Fall 2010}{ITG Canada Inc.}{Trading System/Compliance Analyst}{Toronto ON}{}{
	During my first 4-month block at ITG, I used a combination of Excel, SQL, VBA and Ruby to provide generic compliance support for institutional trading activity.
	During my second block, I independently completely overhauled the existing trade compliance infrastructure in \textbf{SQL}---automating away the business case for hiring me in the first place.
}

\clearpage

\section{Projects}

\cventry{2015}{Cacophony: Real-Time Audio Synthesis}{}{}{}{
  This project was spawned from my desire to both learn a new languange (Haskell), and write a low-level midi synthesizer.
  It deserves a place here not due to results; but rather the sheer number of false starts, language swaps; and general shenanigans that it took to realise that this sort of thing is actually difficult to get right.
  This project is currently halted untill I can find sufficient time to fix/maintain a bunch of sound-related Haskell libraries (I'm looking at \emph{you} portaudio, lib-sndfile, repa).
}

\cventry{2013-2014}{Relay: Adaptive Traffic Control}{SYDE 4B Design Project}{}{}{
	Traffic is a significant problem in almost all urban areas.
	We designed a distributed traffic control system composed of single-intersection agents married to a modern traffic visualization application.
	I designed the control systems, network architecture, and incentive structures used in the project.
  The actors in the system (implemented in \textbf{Erlang/OTP}) operated as dynamic graph automata with consensus filters for loose synchroneity.
}

\cventry{Winter 2014}{Attention: English Accent Classification}{Research/Vision Quest}{}{}{
  Speech recognition is hard, particularly given the wide gamut of accents (even for humans!).
  Using a variety of signal processing techniques, as well as some unsupervised learning, I developed a system which can (poorly) classify whether a speaker is a native to the language.
  The system was written in \textbf{Python} making extensive use of \textbf{SciKit Learn}, and \textbf{NumPy}.
}

\cventry{Winter 2013}{divie: Friendly Asset Division}{SYDE 3B Design Project}{Waterloo ON}{}{
	Divie is a generalised auction/assignment platform targeted at division-of-asset scenarios (such as divorce).
  Each user allocates a fixed budget towards items in a silent-auction-like manner.
  I architected the system, and designed an algorithm which distributes auction items so that the variance of loss across the stakeholders is minimized.
  The application was powered by \textbf{Flask, PostgresSQL}, and \textbf{Heroku}.
}

\cventry{Fall 2012}{BufferBox Lock Addressing}{BufferBox Inc.}{Waterloo ON}{}{
	In partnership with BufferBox (YC'12)---a Waterloo-based logistics and delivery company (acquired by Google), we implemented the hardware aspect of the BufferBox platform using open-source components and software (Arduinos and LAMP). I worked primarily in \textbf{C++}.}

%Section
\section{Formal Education}
\cventry{2009-2014}{BASc, Hon. Systems Design Engineering}{University of Waterloo}{}{Canada}{}
\cventry{2005-2009}{IB Diploma and OSSD}{Vaughan Road Academy}{Toronto}{Canada}{}

%Section
\section{Vices}
\cvline{Music}{Piano, Saxophone, Guitar, Didgeridoo}
\cvline{}{Improvisational Jazz}
\cvline{Fitness}{Running, Climbing, Cycling, Sailing}
\cvline{Computing}{Auctions, Markets, Synthesizers}
\cvline{Misc.}{Strategic Board Games, Cooking}

\closesection{}
\renewcommand{\listitemsymbol}{-}
\end{document}
